Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2021-10-24 article.rnw
MMove the title onto its own page, as required by the journal style.
Move figures to the end of the document, as required by the journal style.
This is done using the endfloat package, creating some new intermediate files.
As such, the make clean rule and the gitignore files have also been updated.
Add author affiliation.
Rearrange the preamble with section header comments.
Set the page size and font size the journal requires.
Add line numbers and double spacing.
Begin page numbering from the title page.
COnfigure endfloat to handle tables.
Add a list of key words to the article.

\documentclass[a4paper,11pt]{article}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{import}

\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{colortbl}

@@

%Title Page
\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
\author{
	Christopher R. P. Brown
}
\date{}

@@

@@

>>>>

\documentclass[12pt,titlepage]{article}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{import}
\usepackage{authblk}

%Images
\usepackage{subcaption}
\usepackage{pgfplots}
\usepackage{colortbl}

%Journal font & paper requirements
\usepackage{newtxtext} %Times New Roman
\usepackage[letterpaper,margin=1in]{geometry}

%Preprint
\usepackage{lineno} \linenumbers
\usepackage{setspace} \doublespacing
\usepackage[nomarkers,tablesfirst,notablist]{endfloat}
\addtodelayedfloat{figure}{\clearpage} %Each delayed figure on a new page.

%Ensure title page is numbered, as journal style requires it.
%Using https://tex.stackexchange.com/a/172005, adapted not to bother with two column stuff.
\makeatletter
\renewenvironment{titlepage}{\thispagestyle{plain}}{\newpage}
\makeatother

@@

%Title Page
\title{Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable}
\author{Christopher R. P. Brown}
\affil{Centre for Integrative Ecology, School of Biological Sciences, University of Canterbury, Christchurch, New Zealand}
\date{}

@@

\newcommand\keywords[1]{\emph{Key words: #1}}

@@

\keywords{Lotka--Volterra; interaction matrix; competition; grouping; model fitting; parsimony; phylogeny}
